Inferring the Recombinant Genealogy of a Pandemic Pathogen in Real Time

### 2025-09-03 latex/main.tex
Some analysis

% This table is generated by the notebook tab_pango_x_events
\begin{table}
\caption{ARG events associated with Pango X lineages.
Each row corresponds to the oldest node assigned the specified
Pango lineage and the ancestor of all nodes assigned that label
(except XBB, XBB.1 and XM; see STAR methods). [MORE DETAILS]
\label{tab:pango_x_lineages}}
\begin{tabular}{lrlrrrrr}
\toprule
pango & samples & extra & muts & root & recomb & t recomb & p recomb \\
\midrule
XA & 39 & \{\} & 1 & 122444 & 122444 & 0 & 0 \\
XBB & 6452 & \{BA.2:1\} & 14 & 1396207 & 1396207 & 0 & 0 \\
XBB.1 & 2 & \{\} & 1 & 1429711 & 1429711 & 0 & 0 \\
XBD & 30 & \{\} & 0 & 1378208 & 1378208 & 0 & 0 \\
XBF & 185 & \{\} & 3 & 1420385 & 1420385 & 0 & 0 \\
XBG & 25 & \{\} & 2 & 1291970 & 1291970 & 0 & 0 \\
XBR & 1 & \{\} & 2 & 1420166 & 1420166 & 0 & 0 \\
XC & 5 & \{\} & 1 & 414488 & 414488 & 0 & 0 \\
XF & 16 & \{\} & 1 & 946761 & 946761 & 0 & 0 \\
XG & 3 & \{\} & 3 & 1083412 & 1083412 & 0 & 0 \\
XL & 64 & \{\} & 1 & 1034619 & 1034619 & 0 & 0 \\
XM & 26 & \{BA.2:16, XAL:3\} & 0 & 1003220 & 1003220 & 0 & 0 \\
XQ & 55 & \{BA.2:37, $\star$\} & 3 & 1058654 & 1058654 & 0 & 0 \\
XS & 17 & \{\} & 1 & 1000242 & 1000242 & 0 & 0 \\
XW & 32 & \{\} & 1 & 1159411 & 1159411 & 0 & 0 \\
XY & 23 & \{\} & 2 & 1187989 & 1187989 & 0 & 0 \\
\midrule
XAA & 17 & \{\} & 3 & 1183815 & 1058654 & 33 & 6 \\
XAE & 9 & \{\} & 7 & 1118099 & 964555 & 47 & 2 \\
XAF & 1 & \{\} & 8 & 1314603 & 1177107 & 140 & 5 \\
XAG & 6 & \{\} & 4 & 1248341 & 1058654 & 55 & 6 \\
XAL & 3 & \{\} & 2 & 1264107 & 1003220 & 66 & 3 \\
XAM & 21 & \{\} & 3 & 1240312 & 1058654 & 43 & 6 \\
XAN & 7 & \{\} & 5 & 1301399 & 1189192 & 114 & 4 \\
XAP & 20 & \{\} & 1 & 1216836 & 964555 & 67 & 4 \\
XAV & 13 & \{\} & 3 & 1269391 & 1189192 & 106 & 7 \\
XAZ & 133 & \{\} & 3 & 1285706 & 1189192 & 62 & 2 \\
XBE & 65 & \{\} & 3 & 1363926 & 1189192 & 136 & 6 \\
XBH & 2 & \{\} & 2 & 1395926 & 1379419 & 27 & 1 \\
XBM & 10 & \{\} & 1 & 1358392 & 1348822 & 23 & 1 \\
XE & 1116 & \{\} & 2 & 965352 & 965353 & 19 & 1 \\
XH & 2 & \{\} & 7 & 1098084 & 965353 & 55 & 1 \\
XJ & 68 & \{BA.2:3\} & 2 & 966904 & 966905 & 5 & 1 \\
XR & 17 & \{BA.2:1\} & 4 & 1148222 & 1058654 & 11 & 3 \\
XU & 1 & \{\} & 4 & 1243765 & 1058654 & 103 & 6 \\
XZ & 48 & \{\} & 1 & 1163537 & 964555 & 48 & 4 \\
\midrule
XAJ & 18 & \{\} & 11 & 1276376 & -1 & inf & inf \\
XAS & 77 & \{\} & 1 & 1265115 & -1 & inf & inf \\
XAU & 8 & \{\} & 1 & 1231548 & -1 & inf & inf \\
XB & 192 & \{\} & 2 & 223239 & -1 & inf & inf \\
XBK & 7 & \{\} & 1 & 1425824 & -1 & inf & inf \\
XBQ & 14 & \{\} & 1 & 1422955 & -1 & inf & inf \\
XN & 120 & \{BA.2:1\} & 1 & 1061700 & -1 & inf & inf \\
XP & 45 & \{\} & 1 & 1092789 & -1 & inf & inf \\
\bottomrule
\end{tabular}
\end{table}

>>>>

% This table is generated by the notebook tab_pango_x_events
\begin{table}
\caption{ARG events associated with Pango X lineages.
Each row corresponds to the oldest node assigned the specified
Pango lineage and the ancestor of all nodes assigned that label
(except XBB, XBB.1 and XM; see STAR methods). [MORE DETAILS]
\label{tab:pango_x_lineages}}
\begin{tabular}{lrrrrl}
\toprule
\multicolumn{5}{l}{Type I RE event: monophyletic for pango}\\
pango & averted & left & right & samples & nested \\
\midrule
XC & 37 & 26768 & 27390 & 5 & \{\} \\
XBR & 22 & 22034 & 22190 & 1 & \{\} \\
XA & 16 & 20411 & 21765 & 39 & \{\} \\
XS & 11 & 9054 & 10449 & 17 & \{\} \\
XL & 8 & 5925 & 8393 & 64 & \{\} \\
XBG & 8 & 22305 & 22917 & 25 & \{\} \\
XBD & 7 & 23020 & 24620 & 30 & \{\} \\
XQ & 7 & 4322 & 5386 & 55 & \{BA.2:37, $\star$\} \\
XBB & 6 & 22332 & 22577 & 6452 & \{BA.2:1\} \\
XM & 6 & 17411 & 21595 & 26 & \{BA.2:16, XAL:3\} \\
XBF & 5 & 5184 & 9866 & 185 & \{\} \\
XF & 5 & 5387 & 6402 & 16 & \{\} \\
XY & 5 & 11538 & 12880 & 23 & \{\} \\
XG & 4 & 5925 & 6513 & 3 & \{\} \\
XW & 4 & 2833 & 4321 & 32 & \{\} \\
\midrule
\multicolumn{5}{l}{Type II RE event}\\
alias & averted & left & right & total & by pango \\
\midrule
XAE+ & 6 & 24504 & 26060 & 253 & {BA.2:156, XZ:48, XAP:20, XAC:18, XAE:9, XAD:2} \\
XE/XH & 6 & 10448 & 11283 & 1156 & {XE:1116, BA.2:37, XH:2, XAF:1} \\
XBH & 6 & 15452 & 22001 & 6 & {BA.2:4, XBH:2} \\
XBM & 6 & 22305 & 22917 & 12 & {XBM:10, BF.3:2} \\
XAF & 5 & 10199 & 10447 & 36 & {BA.2:35, XAF:1} \\
XJ & 5 & 13196 & 17410 & 85 & {XJ:68, BA.2:17} \\
\bottomrule

\end{tabular}

\end{table}
